Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-20 journal/article.tex
Success: Requirements handling

@@

>>>>

* Definition of product owner

@@

\subsubsection{Considering other parts than development}

% Improve requirements handling

Some cases reported on challenges in requirements management, especially
highlighting difficulty in managing the gap between high level requirements and
stories handled by teams. It was stated that it is important that the
requirements are consise and small enough for the teams to handle [P5, P11].
It was recommended to invest in teaching skills in breaking down and writing
user stories [P11, P33, P48]. Gat [P17] describes how the gap between
development and requirements management was bridged by having a dedicated
Requirements Architect to help with requirements breakdown.
